Attack Graph Generation for Microservice Architecture

### 2018-09-23 paper_own_docker/chapters/evaluation.tex
reductions

Modern microservice architectures use an abundance of different technologies,  number of containers, various connectivity and number of vulnerabilities. Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios. In order to do this, we tested our system on real and slightly modified Github examples as described in Table \ref{table_technologies}. Our intention was to find and test examples that are publicly available for possible future comparison characterized by different system properties (topologies, technologies, vulnerabilities) and coming from different usage domains. We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or a few containers, which made this search challenging. The resulting examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo. NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses many tools like Spring Cloud, Netflix Ribbon, and Netflix Eureka. Atsea Sample Shop App is an e-commerce sample web application composed of 4 containers and uses Spring Boot, React, NGINX and PostgreSQL. JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE. We ran the attack graph generator and verified the resulting attack graphs of the small examples manually based on domain knowledge and under the assumption that the output from Clair \cite{clair}, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al. \cite{aksu2018automated} are \textit{correct}. After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo are small as expected with few nodes and edges. The structure of the resulting Netflix attack graph had a nearly linear structure in which each node is connected to a small number of other nodes that form a chain of attacks. This linearity is because each container is connected to a few other containers to reduce unnecessary communication and increase encapsulation. Therefore, based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container. All of the examples terminated, there are no directed edges from containers with higher privileges to lower privileges, no duplication of nodes and no reflexive edges, which is in line with the previously mentioned monotonicity property. Additionally, we noticed that the running time of our system for each of these examples was short, and additional scalability tests are needed. The Phpmailer and Samba  system is an artificial example that we use and extend in the following subsection to perform these scalability tests.

>>>>

Modern microservice architectures use an abundance of different technologies,  number of containers, various connectivity and number of vulnerabilities. Therefore it is of immense importance to show that an attack graph generator works well in such heterogeneous scenarios. In order to do this, we tested our system on real and slightly modified Github examples as described in Table \ref{table_technologies}. Our intention was to find and test examples that are publicly available for possible future comparison characterized by different system properties (topologies, technologies, vulnerabilities) and coming from different usage domains. We also had to take into account that an overwhelming majority of the examples publicly available are small with only one or a few containers, which made this search challenging. The resulting examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo. NetflixOSS is a microservice system provided by Netflix that is composed of 10 containers and uses many tools like Spring Cloud, Netflix Ribbon, and Netflix Eureka. Atsea Sample Shop App is an e-commerce sample web application composed of 4 containers and uses Spring Boot, React, NGINX and PostgreSQL. JavaEE demo is a sample application for browsing movies that is composed of only two containers and uses JavaEE, React and Tomcat EE. We ran the attack graph generator and verified the resulting attack graphs of the small examples manually based on domain knowledge and under the assumption that the output from Clair, NVD attack vectors \cite{booth2013national} and the pre- and postconditions from the work of Aksu et al. \cite{aksu2018automated} are \textit{correct}. After running the attack graph generator, the attack graphs for the Atsea Sample Shop app and the JavaEE demo are small as expected with few nodes and edges. The structure of the resulting Netflix attack graph had a nearly linear structure in which each node is connected to a small number of other nodes that form a chain of attacks. This linearity is because each container is connected to a few other containers to reduce unnecessary communication and increase encapsulation. Therefore, based on this connectivity an attacker needs to perform multiple intermediate steps in order to reach the target container. All of the examples terminated, there are no directed edges from containers with higher privileges to lower privileges, no duplication of nodes and no reflexive edges, which is in line with the previously mentioned monotonicity property. Additionally, we noticed that the running time of our system for each of these examples was short, and additional scalability tests are needed. The Phpmailer and Samba  system is an artificial example that we use and extend in the following subsection to perform these scalability tests.

### 2018-09-23 paper_own_docker/chapters/introduction.tex
reductions

% the problem: summing it up and the solution
% the potentisl benefit in the scope of devops practices and automation (automation should be mentioned before)
% contribution  focus on docker and MS in comparison with networks and normal systems and maybe the github
Previous work has dealt with automatic attack graph generation, exclusively in computer networks \cite{ingols2006practical, sheyner2002automated,  sheyner2003tools, ou2006scalable}. In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining privileges of a specific host. Tools that scan the vulnerabilities of a specific host are available \cite{farmer1990cops}, but they are not sufficient to analyze the security of an entire network, and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.

>>>>

% the problem: summing it up and the solution
% the potentisl benefit in the scope of devops practices and automation (automation should be mentioned before)
% contribution  focus on docker and MS in comparison with networks and normal systems and maybe the github
Previous work has dealt with automatic attack graph generation, exclusively in computer networks \cite{ingols2006practical, sheyner2002automated, ou2006scalable}. In these networks, an attacker performs multiple steps to achieve his goal, e.g., gaining privileges of a specific host. Tools that scan the vulnerabilities of a specific host are available \cite{farmer1990cops}, but they are not sufficient to analyze the security of an entire network, and the possible composition of various vulnerability exploitation as an attack path \cite{sheyner2002automated}.

### 2018-09-23 paper_own_docker/chapters/method.tex
reductions

Another consideration that we take into account is the \textit{privileged access} \footnote{\url{http://obrown.io/2016/02/15/privileged-containers.html}} \cite{libvirt}. Some containers obtain certain privileges that grant them control over the docker daemon in order to function properly. For example, a user may want to run some hardware (e.g., web-cam) or some applications that demand higher privilege levels  from Docker. In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file. An attacker with access to these containers has also access to the Docker daemon. Once the attacker has access to the Docker daemon, he has potential access to the whole microservice system, since every container is controlled and hosted by the daemon.

>>>>

Another consideration that we take into account is the \textit{privileged access} \footnote{\url{http://obrown.io/2016/02/15/privileged-containers.html}}. Some containers obtain certain privileges that grant them control over the docker daemon in order to function properly. For example, a user may want to run some hardware (e.g., web-cam) or some applications that demand higher privilege levels  from Docker. In Docker, this is usually done either by mounting the Docker socket or specifying the keyword "privileged" in the docker-compose.yml file. An attacker with access to these containers has also access to the Docker daemon. Once the attacker has access to the Docker daemon, he has potential access to the whole microservice system, since every container is controlled and hosted by the daemon.

### 2018-09-23 paper_own_docker/main.tex
Todos in method and evaluation done
intro draft
fixes here and there
checks here and there
An example precondition rule added, figure changed and the algorithm now has numbers and they are referenced in the text.
reductions

\usepackage{booktabs} % For formal tables
\usepackage[]{algorithm2e}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{xx.xxx/xxx_x}

@@

\begin{document}
\title{Attack Graph Generation for Micro-service
	Architecture}
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}

\author{Amjad Ibrahim}
\affiliation{\institution{Technical University of Munich}}
\email{amjad.ibrahim@tum.de}

@@

\author{Prof. Dr. Alexander Pretschner}
\affiliation{\institution{Technical University of Munich}}
\email{alexander.pretschner@tum.de}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{B. Trovato et al.}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{Attack Graph Generaton, Computer Security, Microservices}

\maketitle
\input{./chapters/introduction}
\input{./chapters/background}
\input{./chapters/method}
\input{./chapters/evaluation}
\input{./chapters/related_work}
\input{./chapters/conclusion}
\input{./chapters/future_work}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

>>>>

\usepackage{booktabs} % For formal tables
\usepackage[linesnumbered]{algorithm2e} 
\usepackage{subcaption}
% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}

% DOI
\acmDOI{xx.xxx/xxx_x}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

@@

\def\anonymous{}
\begin{document}
\title{Attack Graph Generation for Microservice
	Architecture}

\ifdefined\anonymous
\author{Anonymized  author(s)}
\else
\author{Amjad Ibrahim}
\affiliation{\institution{Technical University of Munich}}
\email{amjad.ibrahim@tum.de}

@@

\author{Alexander Pretschner}
\affiliation{\institution{Technical University of Munich}}
\email{alexander.pretschner@tum.de}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{A. Ibrahim et al.}
\fi

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\iffalse
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}
\fi

\keywords{Attack Graph Generaton, Microservices, Containers}

\maketitle
\input{./chapters/introduction}
\input{./chapters/background}
\input{./chapters/method}
\input{./chapters/evaluation}
\input{./chapters/related_work}
\input{./chapters/conclusion}
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}
